NURM: a tool to locate numerical differences in pipelines

### 2019-05-17 paper.tex
Edited tool description

Figure~\ref{fig:overview} shows an overview of our method.
For each tested condition, the
pipeline is containerized using Docker, and its interface is
described using Boutiques~\cite{glatard2017boutiques}. \reprozip
is added to the container images for provenance tracking. Our tool first
clusters the subjects based on the similarity of their process trees
produced by \reprozip (Fig.~\ref{fig:overview-cluster}). This results in a
reduced set of representative process trees to evaluate. The processes in
each representative process tree are labeled \tristan{Replace
``classification'' by ``labelling'' everyrwhere} from potential differences
found in their outputs produced in the tested conditions (Fig.~\ref{fig:overview-classify}).
To do that, a difference file is first produced that contains all the
files with differences across conditions
(Fig.~\ref{fig:overview-classify} - (A)\tristan{Add labels to the figure}).
Differences are identified simply by comparing file checksums. Using the
difference file, we then classify processes in 4 categories (Fig.~\ref{fig:overview-classify} - (B)) depending
whether they create differences (represented in red), remove differences
(blue), neither create nor remove differences (green), or have uncertain
behavior (yellow). When processes with an uncertain behavior are found, the
pipeline in condition 2 is modified (as explained later) and re-executed. This
procedure iterates until all processes are classified. 
\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=.7\columnwidth]{images/Slide1}
    \caption{Subject clustering.}
    \label{fig:overview-cluster}
  \end{subfigure}
   \begin{subfigure}{\columnwidth}
    \centering
     \includegraphics[width=.75\columnwidth]{images/Slide2}
     \caption{Process classification.}
     \label{fig:overview-classify}
   \end{subfigure}
   \caption{Method overview}
   \label{fig:overview}
  \end{figure}

>>>>

Figure~\ref{fig:overview} shows an overview of our method.
For each tested condition, the
pipeline is containerized using Docker, and its interface is
described using Boutiques~\cite{glatard2017boutiques}. \reprozip
is added to the container images for provenance tracking. Our tool first
clusters the subjects based on the similarity of their process trees
produced by \reprozip (Fig.~\ref{fig:overview-cluster}). This results in a
reduced set of representative process trees to evaluate. The processes in
each representative process tree are labeled \tristan{Replace
``classification'' by ``labelling'' everyrwhere} from potential differences
found in their outputs produced in the tested conditions (Fig.~\ref{fig:overview-classify}).
To do that, a difference file is first produced that contains all the
files with differences across conditions
(Fig.~\ref{fig:overview-classify} - (A)\tristan{Add labels to the figure}).
Differences are identified simply by comparing file checksums. Using the
difference file, we then label processes in 4 categories (Fig.~\ref{fig:overview-classify} - (B)) depending
whether they create differences (represented in red), remove differences
(blue), neither create nor remove differences (green), or have uncertain
behavior (yellow). When processes with an uncertain behavior are found, the
pipeline in condition 2 is modified (as explained later) and re-executed. This
procedure iterates until all processes are labeled. 
\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=.7\columnwidth]{images/Slide1}
    \caption{Subject clustering.}
    \label{fig:overview-cluster}
  \end{subfigure}
   \begin{subfigure}{\columnwidth}
    \centering
     \includegraphics[width=.75\columnwidth]{images/Slide2}
     \caption{Process classification.}
     \label{fig:overview-classify}
   \end{subfigure}
   \caption{Method overview}
   \label{fig:overview}
  \end{figure}
